

Derandomized mutation performs better on the following functions: (initial variance is 5, mutation prob is 0.8, crossover is  SBX-5 and Pr(0.8))
\begin{itemize}
\item Rosenbrock function 28.
\item Function 23
\item Much better on functions 26 \& 34
\item Function 2
\end{itemize}
By using $\alpha = 80$ and offsprings 30, better results were obtained for the following functions:
\begin{itemize}
\item function 13 (as well as function 12)
\item function 16
\item function 19
\item 2-moderate 4-multi-modal:  no good results in function group overall except for a slight improvement with this configuration on function 25
\end{itemize}

Function 15: Isotropic : Variance of 5 better than variance of 10, 
			 Derandomized: Smaller population as good as isotropic with small variance
			 
\subsubsection*{1-separable 2-moderate (3d)}: 
low mutation (0.1) is better for functions 12 and 13 and/or high recombination probability (>=0.8) is bad (why?)

smaller initial variance (3) is better for f13

\subsubsection*{1-separable 4-multi-modal} : high variance (10) is bad

\subsubsection*{1-separable 5-weakly-structured}
function 18: High recombination probability (0.7-0.9)
			  High mutation probability (around 0.7-0.8)  (along with isotropic pop 100)
			  High variance is bad

\subsubsection*{2-moderate 2-moderate}
Variance is a critical factor. 
Mutation with probability 1 without adaptation of the variance gives worse results.
Function 20 gives good results with mut0.3 in 5d - best mut0.3 recomb0.7 
28-2d as good for pop100 offs20 mut0.1 recomb0.7 var5.0 as for pop100 offs20 mut0.8 recomb0.6

\subsubsection*{2-moderate 5-weakly-structured}
Better results with low mutation probability (0.1-0.3)
Function 33: good results with relatively higher variance. Improved for a smaller population and moderate variance
26, 33: best with mut0.8 recomb0.6

\subsubsection*{3-ill-conditioned 3-ill-conditioned} 
variance is not the determinating factor. Isotropic a little worse.

Function 42: Derandomized and/or Higher population are better than pop=60

\subsubsection*{3-ill-conditioned 5-weakly-structured} 
High variance doesn't hurt w.r.t a smaller one. - 
Can't say much though because the problems are unstructured and hard)
f44-5d: mut0.8 recomb0.7 var5.0derandomized sbx2

\subsubsection*{4-multi-modal 4-multi-modal} 
Derandomized improves a tiny bit on isotropic.
\subsubsection*{4-multi-modal 5-weakly-structured}
 Function 48: high variance does not perform worse, on other functions of  derandomized is better
								    
Functions 54, 55: Can't say much. Derandomized/Smaller variance better.

Cases in which low mutation probability works:
2-moderate 5-weakly-structured: best is 0.3
3-ill-conditioned 5-weakly-structured: function 44 has good results

For 5-d space:
Function 53 performs very well with pop80, mut0.8, recombination1.0, derandomized
On the other hand it performs well with low mutation probability (0.1-0.3) on 3d
Find solutions really quick with var 3.
